### 2024-03-27 tesis_Ashish/Chapter5/chapter5.tex
update 27 Mar

To investigate the performance of the PCC luminometer during the 2022 data collection period \cite{Hayrapetyan:2870088}, we segment CMS luminosity data into five distinct periods:  C, D, E, F, and G, as illustrated in Figure \ref{fig:period_bound_1}. The run ranges associated with each of these periods are outlined in Fig. \ref{fig:period_bound_1}. Notably, during period F, specifically during Fill 8381, van der Meer (vdM) scans were implemented to calibrate the PCC luminometer. For our current analysis, we employ dataset that align with the 2022 luminosity measurement periods, specifically 2022C, 2022D, 2022E, and 2022F, Run 2022G as highlighted in Table \ref{tab:my_label_1}. We extracted these datasets from the Alignment and Calibration (AlCa) project, a critical aspect of the CMS experiment. The selected datasets encompass two subcategories, namely Random trigger and Zero Bias similar to Run 2 PCC dataset. %The Random trigger dataset includes data where triggers are applied to both colliding and non-colliding bunches and the Zero Bias dataset consists of events that have successfully navigated the trigger system without any bias (no use of CMS detector signal), in this case, the trigger is applied exclusively to the colliding bunches.

@@

\begin{table}[h]
  \centering
  \caption[2022 run ranges]{Run periods, run number ranges and dates.}
\begin{tabular}{ccc}
%\hline
\textbf{Run Period} & \textbf{Run Number Range} & \textbf{Date} \\
\hline
C & 355862 - 357401 & 2022-07-19 to 2022-08-12 \\
%\hline
D & 357538 - 357900 & 2022-08-15 to 2022-08-23 \\
%\hline
E & 359268 - 360327 & 2022-09-23 to 2022-10-14 \\
%\hline
F & 360390 - 362167 & 2022-10-14 to 2022-11-17 \\
%\hline
G & 362433 - 362760 & 2022-11-21 to 2022-11-28 \\
%\hline
\end{tabular}
%\caption[Run period details]{Run periods, run number ranges and dates.}
\label{tab:my_label_1}
\end{table}

@@

Table \ref{tab:2022ldmodules} presents the number of good modules in various layers and disks of the pixel detector after a final selection process. Layer 3 has 39 good modules, Layer 4 has 88, Disk 1 has 13, Disk 2 has 19, and Disk 3 has 4, totaling 163 modules. The stability of various pixel layers and disks after removing all modules in Layer 0 and for final veto are shown in Fig. \ref{fig:stabprof_69a}  and Fig. \ref{fig:stabprof_69b} respectively.

@@

\begin{figure}[!htp]
  \centering
  \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_stability_2022_L0veto_4.png}
  \caption[Luminosity Fractions w/o Layer 0 Modules]{Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for the entire 2022 data with all Layer 0 modules vetoed.}
  \label{fig:stabprof_69a}
\end{figure}

\begin{figure}[!htp]
  \centering
  \includegraphics[width=0.7\textwidth]{ashish_thesis/2022_pcc_stability_2.png}
  \caption[Stability Profiles For Final Veto]{Stability profiles of pixel detector layer and disk modules for the final module veto list.}
  \label{fig:stabprof_69b}
\end{figure}

@@

van der Meer (vdM) scan was performed in November 2022, during the LHC fills 8379 and 8381. In fill 8381 on 10–11 Nov 2022, data was collected when 144 paired bunches of particles were colliding, with additional unpaired bunches also present, various scan pairs were conducted, including four vdM scans, two Beam Imaging (BI) scans, and one length scale scan. Each of these scans consists of two examinations in the x and y transverse planes. In the vdM scan, beams were separated by a distance correlating to six times transverse beam size and then moved across each other in 25 steps. Each step lasted 30 seconds and moved the beams by half of their transverse size. For the BI scans, one beam remained fixed while the other moved in 19 steps, over a distance of up to 4.5 times its transverse size. The length scale scan involved beams being separated by a constant distance and moved in both directions in five steps. The scan program during Fill 8381 is shown in Fig. \ref{fig:2022_vdM_program}.

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM.png}
\caption[2022 vdM Program]{%                                                                                                                                             
  2022 vdM calibration program. In LHC fill 8381, proton beam positions were recorded, including four vdM scans, two BI scans, one LS scan, and two SS periods.
}
\label{fig:2022_vdM_program}
\end{figure}

@@

The result of the calibration is described in
%Normalized Rates and Resulting Fitted Double Gaussian Scan Curves for Single Bunch in X and Y Directions:
Figure \ref{fig:period_bound_50} which depict how the detected event rate varies as the beams are scanned across each other in the horizontal (X) and vertical (Y) directions.The rates have been fitted to a double Gaussian curve, which reflects the bell-shaped spatial distribution of the proton bunches. The peaks of these curves correspond to the maximum event rate, which occurs when the beams are perfectly overlapped. The width of the curve gives an indication of the spread of the beam in the respective direction. In the final analysis. a floating constant is used in the fit for the background because the background from the SS1 and SS2 give inconsistent values as shown in Table \ref{table:side_by_side}.

%Background subtraction and beam corrections have been applied to the raw data to account for noise.
%Chi2/ndof for all vdM and Imaging Scans:
%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit. A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit. PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb. The bunch to bunch variation and scan to scan variation of PCC visible cross section is shown in Fig. \ref{fig:period_bound_99} and Fig. \ref{fig:period_bound_105} \cite{pas_22} %\cite{bril2023vdmrecalibration}.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_PCC_sigmavis_per_scan_new.png}
\caption[2022 PCC Visible Cross Section]{%                                                                                                                                                                               
  Visible cross section per scan where red line shows the average value. Red band depicts the RMS of the values.
}
\label{fig:period_bound_105}
\end{figure}

@@

The Fill cycle in Run 3 includes a leveling part in order to control the very high pileup achieved with upgraded LHC beam optics. The Fill luminosity profile for Fill 8274 during 2022 data taking is shown in Fig. \ref{fig:period_bound_111}. This Fill consists of

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Fill_profile_8274_1.png}
\caption[Fill 8274 Luminosity Profile]{%                                                                                                                                                                                         
  PCC luminosity profile for Fill 8395.
}
\label{fig:period_bound_111}
\end{figure}

@@

Type-2 parameters, derived from a preceding study using Random trigger data, are presumed to remain constant during the year. The fitting template is given by:
\begin{equation}
F(x) = \Sigma_{k=0}^{N_{bcid}} N_k \left[(x-k==0)+\alpha\cdot(x-k==1)+A \cdot e^{-\tau\cdot(x-k-1)}(x-k>=1) \right]
\end{equation}
with $k$ denoting the colliding bunch crossing and $x$ indicating the histogram bin. 2022 PCC afterglow model uses run number 361957 for doing fit to type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig. \ref{fig:period_bound_101}. Model consist of a parameter for type 1 afterglow correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction. Fit function is summed over all bunch crossings. Fit perfomed for 4 wagon train is shown in Fig.  \ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width. The values obtained for type 2 afterglow amplitude and decay parameters are 0.0008406 and 0.01047 respectively \cite{pas_22}. %\cite{bril2023afterglow}.
%as shown in Table. \ref{table:trains_data}.

@@

\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another. Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing. %These variations are important to monitor as they can impact the precision of the luminosity measurement, which in turn affects the accuracy of the results obtained from the physics analyses conducted with the data.
If significant variations are observed, it may be necessary to adjust the analysis to account for these differences.

@@

\begin{table}[!htp]
  \centering
  \caption[Bunch uncertainty]{Bunch to bunch variation of visible cross section (as shown in Fig. \ref{fig:period_bound_99}). $N_b$ is the number of bunches in the vdM scan. SEM is the standard error on the mean.}
\begin{tabular}{cccc}
\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & (SEM/$\sigma_{vis}$) [\%] \\
\hline
vdM1 & 1065.09 & 2.89 & 0.1286 \\
Img1 & 1070.14 & 3.94 & 0.1746 \\
Img2 & 1075.38 & 2.35 & 0.1040 \\
vdM3 & 1083.58 & 3.70 & 0.1616 \\
vdM4 & 1080.37 & 2.09 & 0.0920 \\
\end{tabular}
\label{tab:my_label}
%\caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\end{table}

@@

\newpage
\item Scan to scan uncertainty: PCC visible cross section can exhibit change from one scan to the next. These variations could be due to slight changes in the experimental conditions. The results for each scan are plotted after averaging over five BCIDs. Each point on this graph represent the result from one scan. A red line is drawn to indicate the average value of the visible cross-section over all the scans. This average value provide a useful comparison point to evaluate the consistency of the individual scan results and identify any potential anomalies or systematic errors.

@@

The left plot in figure \ref{fig:stabprof2_2000} provides a comparison of the linearity of PCC luminosity in relation to HFET luminosity. A perfectly linear relationship would imply same luminosity measured by both the luminometers, suggesting an absence of non-linearity in the detector response. The plot in Fig. \ref{fig:stabprof2_2000} shows the ratio of luminosity values obtained using the PCC method to those from the HFET luminometer. The values are plotted as a function of HFET luminosity. The goal of this graph is to examine potential changes in the detector's response across different luminosity levels. If the detector's response was perfectly linear, we do expect the ratio to remain constant across the range of HFET luminosity values. Deviations from a constant ratio indicate non-linearity in the detector response, thereby contributing to systematic uncertainties.

@@

\begin{table}[H]
  \centering
  \caption[Systematic uncertainty in 2022 luminosity measurement]{Systematic uncertainty in 2022 luminosity measurement (\%) \cite{pas_22}}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.2 \\
        Ghost and satellite charges & 0.2 \\
        Orbit drift & 0.1 \\
        Residual beam positions & 0.3 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.6 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.2 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.4 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}

>>>>

To investigate the performance of the PCC luminometer during the 2022 data collection period \cite{Hayrapetyan:2870088}, we segment CMS luminosity data into five distinct periods:  C, D, E, F, and G, as illustrated in Figure \ref{fig:period_bound_1}. The run ranges associated with each of these periods are outlined in Fig. \ref{fig:period_bound_1}. Notably, during period F, specifically during Fill 8381, van der Meer (vdM) scans were implemented to calibrate the PCC luminometer. For our current analysis, we employ dataset that align with the 2022 luminosity measurement periods, specifically 2022C, 2022D, 2022E, 2022F and Run 2022G as highlighted in Table \ref{tab:my_label_1}. We extracted these datasets from the Alignment and Calibration (AlCa) project, a critical aspect of the CMS experiment. The selected datasets encompass two subcategories, namely Random trigger and Zero Bias similar to Run 2 PCC dataset. %The Random trigger dataset includes data where triggers are applied to both colliding and non-colliding bunches and the Zero Bias dataset consists of events that have successfully navigated the trigger system without any bias (no use of CMS detector signal), in this case, the trigger is applied exclusively to the colliding bunches.

@@

\begin{table}[h]
  \centering
  \caption[2022 run ranges]{Run periods, run number ranges and dates for the 2022 data taking period.}
\begin{tabular}{ccc}
%\hline
\textbf{Run Period} & \textbf{Run Number Range} & \textbf{Date} \\
\hline
C & 355862 - 357401 & 2022-07-19 to 2022-08-12 \\
%\hline
D & 357538 - 357900 & 2022-08-15 to 2022-08-23 \\
%\hline
E & 359268 - 360327 & 2022-09-23 to 2022-10-14 \\
%\hline
F & 360390 - 362167 & 2022-10-14 to 2022-11-17 \\
%\hline
G & 362433 - 362760 & 2022-11-21 to 2022-11-28 \\
%\hline
\end{tabular}
%\caption[Run period details]{Run periods, run number ranges and dates.}
\label{tab:my_label_1}
\end{table}

@@

Table \ref{tab:2022ldmodules} presents the number of good modules in various layers and disks of the pixel detector after a final selection process. %Layer 3 has 39 good modules, Layer 4 has 88, Disk 1 has 13, Disk 2 has 19, and Disk 3 has 4, totaling 163 modules.
The stability of various pixel layers and disks after removing all modules in Layer 0 and for final veto are shown in Fig. \ref{fig:stabprof_69a}  and Fig. \ref{fig:stabprof_69b} respectively.

@@

\begin{figure}[!htp]
  \centering
  \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_stability_2022_L0veto_4.png}
  \caption[Luminosity Fractions w/o Layer 0 Modules]{Luminosity fraction of pixel detector for various layers and disks as a function of lumi section for the entire 2022 data with all Layer 0 modules vetoed.}
  \label{fig:stabprof_69a}
\end{figure}

\begin{figure}[!htp]
  \centering
  \includegraphics[width=0.7\textwidth]{ashish_thesis/2022_pcc_stability_2.png}
  \caption[Stability Profiles For Final Veto]{Stability profiles of pixel detector layers and disk modules for the final module veto list.}
  \label{fig:stabprof_69b}
\end{figure}

@@

THe vdM scan was performed in November 2022, during the LHC fills 8379 and 8381. In fill 8381 on 10–11 Nov 2022, data was collected when 144 paired bunches of particles were colliding, with additional unpaired bunches also present. Various scan pairs were conducted, including four vdM scans, two Beam Imaging (BI) scans, and one length scale scan. Each of these scans consists of two examinations in the x and y transverse planes. In the vdM scan, beams were separated by a distance correlating to six times transverse beam size and then moved across each other in 25 steps. Each step lasted 30 seconds and moved the beams by half of their transverse size. For the BI scans, one beam remained fixed while the other moved in 19 steps, over a distance of up to 4.5 times its transverse size. The length scale scan involved beams being separated by a constant distance and moved in both directions in five steps. The scan program during Fill 8381 is shown in Fig. \ref{fig:2022_vdM_program}.

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM.png}
\caption[2022 vdM Program]{%                                                                                                                                             
  2022 vdM calibration program. In LHC fill 8381, proton beam positions were recorded, including four vdM scans, two BI scans, one LS scan, and two SS periods \cite{pas_22}.
}
\label{fig:2022_vdM_program}
\end{figure}

@@

The result of the calibration is described in
%Normalized Rates and Resulting Fitted Double Gaussian Scan Curves for Single Bunch in X and Y Directions:
Figure \ref{fig:period_bound_50} which depicts how the detected event rate varies as the beams are scanned across each other in the horizontal (X) and vertical (Y) directions.The rates have been fitted to a double Gaussian curve, which reflects the bell-shaped spatial distribution of the proton bunches. The peaks of these curves correspond to the maximum event rate, which occurs when the beams are perfectly overlapped. The width of the curve gives an indication of the spread of the beam in the respective direction. In the final analysis. a floating constant is used in the fit for the background because the background from the SS1 and SS2 give inconsistent values as shown in Table \ref{table:side_by_side}.

\begin{table}[!htp]
  \centering
  \caption[2022 PCC background rate]{PCC background rate for five BCIDs during super separation scans 1 and 2. Average PCC background rate is calculated by averaging over all five BCIDs.}
    \begin{minipage}{0.45\textwidth}
        \centering
        \begin{tabular}{ccc}
          \hline
            \multicolumn{3}{|c|}{SS 1} \\
            \hline
            BCID & Mean & SEM \\
            \hline
            282 & 0.03917 & 0.00147 \\
            822 & 0.03896 & 0.00130 \\
            2944 & 0.03979 & 0.00145 \\
            3123 & 0.03788 & 0.00132 \\
            3302 & 0.03931 & 0.00130 \\
        \end{tabular}
        \subcaption{SS1_{avg}= 0.0390 +- 0.000613}
    \end{minipage}%                                                                                                                                                                                                  
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \begin{tabular}{ccc}
            \hline
            \multicolumn{3}{|c|}{SS 2} \\
            \hline
            BCID & Mean & SEM \\
            \hline
            282 & 0.07682 & 0.00128 \\
            822 & 0.077513 & 0.00137 \\
            2944 & 0.082114 & 0.00178 \\
            3123 & 0.075385 & 0.00127 \\
            3302 & 0.077605 & 0.00139 \\
        \end{tabular}
        \subcaption{SS2_{avg}= 0.077902 -+ 0.00060436}
    \end{minipage}
    %\caption{PCC background rate for five BCIDs during super separation scans 1 and 2. Average PCC background rate is calculated by averaging over all five BCIDs.}                                                 
    \label{table:side_by_side}
\end{table}

%Background subtraction and beam corrections have been applied to the raw data to account for noise.
%Chi2/ndof for all vdM and Imaging Scans:
%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit. A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit. The PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb. The bunch to bunch variation and scan to scan variation of the PCC visible cross section is shown in Fig. \ref{fig:period_bound_99} and Fig. \ref{fig:period_bound_105} \cite{pas_22}. %\cite{bril2023vdmrecalibration}.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_PCC_sigmavis_per_scan_new.png}
\caption[2022 PCC Visible Cross Section]{%                                                                                                                                                                               
  Visible cross section per scan where red line shows the average value. Red band depicts the $\pm$ one RMS of the values.
}
\label{fig:period_bound_105}
\end{figure}

@@

The fill cycle in Run 3 includes a leveling part in order to control the very high pileup achieved with upgraded LHC beam optics. The fill luminosity profile for fill 8395 during 2022 data taking is shown in Fig. \ref{fig:period_bound_111}. This fill consists of

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Fill_profile_8274_1.png}
\caption[Fill 8274 Luminosity Profile]{%                                                                                                                                                                                         
  PCC luminosity profile for fill 8395.
}
\label{fig:period_bound_111}
\end{figure}

@@

Type-2 parameters, derived from a preceding study using Random trigger data, are presumed to remain constant during the year. The fitting template is given by:
\begin{equation}
F(x) = \Sigma_{k=0}^{N_{bcid}} N_k \left[(x-k==0)+\alpha\cdot(x-k==1)+A \cdot e^{-\tau\cdot(x-k-1)}(x-k>=1) \right]
\end{equation}
with $k$ denoting the colliding bunch crossing and $x$ indicating the histogram bin. 2022 PCC afterglow model uses run number 361957 for fitting the type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig. \ref{fig:period_bound_101}. The model consists of a parameter for type 1 afterglow correction and an exponentially decaying function with two parameters, amplitude and decay width, to model type 2 afterglow correction. The fit function
%correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction. Fit function
is summed over all bunch crossings. Fit perfomed for 4 wagon train is shown in Fig.  \ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width. The values obtained for type 2 afterglow amplitude and decay parameters are 0.0008406 and 0.01047 respectively \cite{pas_22}. %\cite{bril2023afterglow}.
%as shown in Table. \ref{table:trains_data}.

@@

\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Table \refl{tab:my_labeltt}. Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing. %These variations are important to monitor as they can impact the precision of the luminosity measurement, which in turn affects the accuracy of the results obtained from the physics analyses conducted with the data.
If significant variations are observed, it may be necessary to adjust the analysis to account for these differences.

@@

\begin{table}[!htp]
  \centering
  \caption[Bunch uncertainty]{Bunch to bunch variation of visible cross section (as shown in Fig. \ref{fig:period_bound_99}). $N_b$ is the number of bunches in the vdM scan. SEM is the standard error on the mean.}
\begin{tabular}{cccc}
\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & (SEM/$\sigma_{vis}$) [\%] \\
\hline
vdM1 & 1065.09 & 2.89 & 0.1286 \\
Img1 & 1070.14 & 3.94 & 0.1746 \\
Img2 & 1075.38 & 2.35 & 0.1040 \\
vdM3 & 1083.58 & 3.70 & 0.1616 \\
vdM4 & 1080.37 & 2.09 & 0.0920 \\
\end{tabular}
\label{tab:my_labeltt}
%\caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\end{table}

@@

\newpage
\item Scan to scan uncertainty: PCC visible cross section can exhibit change from one scan to the next. These variations could be due to slight changes in the experimental conditions. The results for each scan are plotted after averaging over five BCIDs as shown in Fig. \ref{fig:period_bound_105}. Each point on this graph represent the result from one scan. A red line is drawn to indicate the average value of the visible cross-section over all the scans. This average value provides a useful comparison point to evaluate the consistency of the individual scan results and identify any potential anomalies or systematic errors.

@@

%The plot in figure \ref{fig:stabprof2_2000} provides a comparison of the linearity of PCC luminosity in relation to HFET luminosity. A perfectly linear relationship would imply same luminosity measured by both the luminometers, suggesting an absence of non-linearity in the detector response.
The plot in Fig. \ref{fig:stabprof2_2000} shows the ratio of luminosity values obtained using the PCC method to those from the HFET luminometer. The values are plotted as a function of HFET luminosity. The goal of this graph is to examine potential changes in the detector response across different luminosity levels. If the detector response was perfectly linear, we do expect the ratio to remain constant across the range of HFET luminosity values. Deviations from a constant ratio indicate non-linearity in the detector response, thereby contributing to systematic uncertainties.

@@

\begin{table}[H]
  \centering
  \caption[Systematic uncertainty in 2022 luminosity measurement]{Systematic uncertainty in 2022 PCC luminosity measurement (\%) \cite{pas_22}}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.2 \\
        Ghost and satellite charges & 0.2 \\
        Orbit drift & 0.1 \\
        Residual beam positions & 0.3 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.6 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.2 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.4 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}
